It still seems that black has hope in these extremely unfair variants of chess

### 2014-03-16 chesstego/paper.tex
Progress on paper

% \begin{itemize} % white
% \end{itemize} % white

@@

\chessboard[setfen=4k3/ppp1pppp/8/8/3p4/2PP4/PP2PPPP/4K3]

>>>>

{\em Chessy Crush Saga} is a hybrid of Chess and the popular and
lucrative phone-game {\em Candy Crush Saga}. In this game, the
regular moves of chess are allowed, but it is also possible to
{\em crush} chess pieces into candies. {\em Chessy Crush v1}
follows the rules of {\em Candy Crush} closely: When a piece moves
such that three pieces of the same color are in a row (either
horizontally or vertically), those pieces are all removed. Usually
this is a tactical misstep in Chess, as three of one's own pieces
are destroyed for nothing. However, as in {\em Candy Crush}, rewards
are given when more than three like pieces are destroyed at once.
The simplest is to award the player with a Candy Rook at at the
place where the moved piece ended up. A Candy Rook moves like a
rook, but if it is crushed, it destroys all of the opponent's
pieces on the file (column) it currently occupies.\!\footnote{In
formal {\em Candy Crush}, this is the vertical striped candy,
which is awarded when the piece was moved vertically. To keep
this variant simple, we always award a ``vertically striped''
Candy Rook, since it seems with only pawns, only vertical moves
are likely. (This later turns out to be a bad assumption.)}

As another simplification, we remove all of the proper pieces from the
black files, except for the King, in honor of the software company
that makes {\em Candy Crush}, ``King.'' A densely packed board with
pieces that can move backward is dangerous, for it is easy to destroy
one's own king by moving out of and then back into the back file,
crushing the whole thing (Figure~\ref{fig:selfcrush}).

\begin{figure}[ht]
\begin{center}
\chessboard[
  setfen=rnbqkbnr/1ppppppp/p7/8/8/8/PPPPPPPP/RNBQKBNR,
  color=black,
  pgfstyle=knightmove,
  markmoves={c3-b1},
  pgfstyle=cross,
  color=red,
  backrank=1]
\end{center}\vspace{-0.1in}
\caption{
  ``Fool's Mate'' in the rejected {\em Candy Crush v0},
  played with normal pieces in the back ranks. White self-mates
  in two moves, crushing all his own pieces {\em e.g.} with:
  1. Nc3 a6 2. Nb1 (??) 0--1
}
\label{fig:selfcrush}
\end{figure}

@@

In {\em v2}, the Candy Rook is extremely powerful, since
not only does it destroy an entire file (the e file being
the likely target, since it contains the immovable King),
but when it is used (by crushing) it is also replaced,
since a crush always yields candy. Therefore, White's
most straightforward strategy is to quickly create a
Candy Rook, then crush it in the e file, which wins. This
should be a line where White's tempo advantage makes it
mostly immune from interference, since even a check is
answered by destroying the opponent's king.

% \chessboard[setfen=4k3/ppp1pppp/8/8/3p4/2PP4/PP2PPPP/4K3]
% \chessboard[setfen=4k3/ppp1pppp/8/8/8/4p3/PP3PPP/4K3]
% \chessboard[setfen=4k3/1ppppppp/8/8/8/8/pR2PPPP/4K3]
\begin{figure}[ht]
\begin{center}
\chessboard[setfen=4k3/3ppppp/1r6/8/8/2R5/PP3PPP/4K3]
(a) \\
\chessboard[
  setfen=4k3/3ppppp/4r3/8/8/8/2R2PPP/4K3,
  pgfstyle=border,
  color=blue!50,
  markfile=e,
  color=black,
  pgfstyle=straightmove,
  markmoves={b6-e6},
  pgfstyle=cross,
  color=red,
  backfields={e8,e7,e6}]
(b)
\end{center}\vspace{-0.1in}
\caption{ 
%
  Black's surprising draw strategy in {\em Chessy Crush v2}. White
  begins her Omega Weapon: 1. e3 c6 2. d3 a6 3. c3 {\em making candy}
  b6 {\em making candy} we have the board in (a). It seems that Black
  is stuck after 4. Rc2, since 5. Re2 will crush White's candy rook
  and destroy the entire e file, including Black's king. Black
  defending with 4. \ldots Re6 initially seems pointless (White will
  destroy the rook as well so the check is irrelevant---this indeed
  refutes 4. \ldots Rb1) but Re6 actually creates a {\em vertical}
  three-piece crush, sacrificing Black's king to destroy the e file
  first, which also destroys White's king! Such mutual destruction
  is not possible in traditional chess, but it seems appropriate to
  consider it a draw in Chessy Crush Saga v2. It appears that White
  can head off this line with 4. Rc8++, a totally vanilla back-rank mate,
  but this is not actually mate with the same 4. \ldots Rb1 escaping
  to a draw.
%
}
\label{fig:chessyv2}
\end{figure}
